### 2024-06-02 2024-5-13/sections/implementation.tex
experiments

\subsection{Empirical evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}}\label{subsec:size_reduction_eval}

@@

\paragraph*{Empirical evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}
We compare $\ostrichrecl$ with its variant  $\ostrichrecl_{\rm +NUXMV}$, which is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the $\cefadec$ problem. Moreover, we also compare $\ostrichrecl$ with its variant $\ostrichrecl_{\rm -ASR}$, which is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 in Section~\ref{subsec:cefadec}).

@@

\begin{table}
  \import{tables}{table_heuristics.tex}
  \caption{Evaluation of the optimizations in Section~\ref{sec:heuristic}}\label{tab:results_heuristic}
\end{table}

@@

\begin{table}
  \import{tables}{table_heuristics_complex.tex}
  \caption{Empirical justification of the optimizations on NestC benchmarks}\label{tab:results_heuristic_complex}
\end{table}

@@

>>>>

\subsection{Evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}}\label{subsec:size_reduction_eval}

@@

\paragraph*{Evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}
%
We compare $\ostrichrecl$ with its variant  $\ostrichrecl_{\rm +NUXMV}$, which is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the $\cefadec$ problem. Moreover, we also compare $\ostrichrecl$ with its variant $\ostrichrecl_{\rm -ASR}$, which is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 in Section~\ref{subsec:cefadec}).

@@

\begin{table}
  \import{tables}{table_heuristics_complex.tex}
  \caption{Evaluation of the optimizations in Section~\ref{sec:heuristic}}\label{tab:results_heuristic_complex}
\end{table}

@@

@@

Table~\ref{tab:results_model-gen}.

\begin{table}
  \import{tables}{table_heuristics_model_gen.tex}
  \caption{Evaluation of the optimizations for the model generation in Section~\ref{sec-opt-sol-gen}}\label{tab:results_model-gen}
\end{table}
